Less is More: Minimizing Code Reorganization using XTREE

### 2017-04-03 doc/Submission rev. 2/Manuscript.tex

\definecolor{steel}{rgb}{0,0,0}
\definecolor{Gray}{rgb}{0.88,1,1}
\definecolor{Gray}{gray}{0.85}
% \usepackage[svgnames]{xcolor}
\usepackage[framed]{ntheorem}
\usepackage{framed}
\usepackage{tikz}
\usetikzlibrary{shadows}
%\newtheorem{Lesson}{Lesson}
\theoremclass{Lesson}
\theoremstyle{break}

@@

			\noindent
			{\bf Results: }Code modules that are changed in response to XTREE's 
			recommendations contain significantly fewer defects than 
			recommendations from previous studies. Further, XTREE endorses 
			changes to very few code metrics, so XTREE requires programmers to do less
                        work. Further, XTREE's recommendations are more 
                        responsive to the
                        particulars of different data sets.

			\noindent
			{\bf Conclusion: }
			Before undertaking a code reorganization based on a bad smell 
			report, use a framework like XTREE to check and ignore any such 
			operations that  are useless; i.e. ones which lack evidence in the 
			historical record  that it is useful to make that change. Note 
			that 
			this use case applies to both manual code reorganizations proposed 
			by developers as well as those conducted by automatic methods. 
			This 
			recommendation assumes that there is an historical record. If none 
			exists, then the results of this paper could be used as a guide 
			(see the last figure of this paper).

@@

	{\color{steel}In terms of concrete recommendations for
		practitioners, we say {\em look before you leap}:
		\bi
		\item Before doing  code reorganization based on a bad smell 
		report$\ldots$ 
		\item $\ldots$ check and discourage any code reorganization   for which 
		there 
		is no proof
		in the historical record that the change improves the code.
		\ei
		Aside: this recommendation   applies to both manual code 
		reorganizations proposed by developers
		as well as the code reorganizations conducted by automatic 
		methods~\cite{mkaouer2015many}. That is, XTREE could optimize automatic
		code reorganization by discouraging reorganizations for useless goals.}

	\section{Relationship to Prior Work }
	{\color{steel}	
	\subsection{Prioritizing Reorganization Efforts}
	\label{sect:prior}

@@

	\subsubsection{XTREE: Recommending Code Reorganizations}

	Using the training data construct a decision tree as suggested above.

@@

	The effect of tuning and using SMOTE were remarkable.The rows 
	\colorbox{celadon}{marked with a $\star$} in \fig{j} show data 
	sets whose performance was improved by these techniques. For 
	example, in {\em poi}, the recall increased by 4\% while the false alarm 
	rate dropped by 21\%. In \textit{Ivy, Jedit, Lucene,} and \textit{Xalan} 
	there was a 
	significant improvement in one measure (recall or false alarm) with no 
	deterioration in the other measure. Finally, in \textit{Poi} and 
	\textit{Ant} there was a significantly large improvement in one metric with 
	a very small deterioration in the other.

	However, as expected, we could not salvage all the data 
	sets. Therefore, we eliminated the data sets for which we could not build 
	an adequately performing Random Forest classifier with $\mathit{pd}\ge 60 
	\wedge \mathit{pf} \le 30$\%. Thus, our analysis uses the {\em jedit, ivy, 
	ant, lucene} and {\em poi} data sets for evaluating recommended changes.}

@@

	\input{rq2.tex}
	\section{Results}

@@

	This is quite significant for practitioners 
	attempting to perform code reorganization to similar projects without a 
	historical log. They can use these findings as guide to: (1) deprecate 
	changes the show no demonstrable benefits; and (2) not limit themselves to 
	reducing values all the metrics because an increase can sometimes be more 
	beneficial.

@@

        In this work, both the primary change oracle and the secondary 
        verification oracle 
        used OO metrics in conjunction with the number of associated defects to 
        operationalize code smells. We note this goal can very easily be 
        replaced by other quantifiable objectives. For example, there is much 
        research on \textit{technical debts} in recent years.
        The notion of technical debt reflects the extra work arising
        from developers making pragmatic short-term decisions
        that make it harder, in the long-term, to maintain the software.
        A recent study by 
        Ernst et al.~\cite{ernst15} showed that practitioners agree on the 
        importance of the issue but existing tools are not currently helpful in 
        managing the debts. A systematic literature survey conducted by Li et 
        al.~\cite{li15td} report that dedicated technical debt management (TDM) 
        tools are needed for managing various types of technical debts. XTREE 
        could be adapted for this purpose-- providing that there existed
        a working ``secondary oracle'' (of the kind we define in our introduction)
        that can recognize quick-and-dirty sections of code.

@@

	\section{Conclusions}
	How to discourage useless code reorganizations?
	We say:
        \begin{quote}{\em Ignore those changes
            not supported by the historical log of data from
	the current project.}\end{quote}
	When that data is not available (e.g. early
	in the project) then developers could use the general list of
	bad smells shown in \fig{smells}. However,
	our results
	show that  bad smell detectors are most
	effective when they are based
	on a small handful of code metrics (as done by XTREE).
	Hence, using all the bad smells of \fig{smells} may not be optimal.

@@

%	
%	
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%	%%% RESPONSE TO REVIEWERS
%	
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%	\pagebreak
%	\newpage
%	\appendix
%	\renewcommand*{\thesection}{\Alph{section}}
%	\nobalance
%	\section*{RESPONSE TO REVIEWERS}
%	\section*{Comments from the editor}
%	\review{The reviewers have finished to  evaluate your work. 
%	As you 
%	can observe, they raised some concerns that deserve your attention~$\ldots$}
%	
%	\noindent Thank you very much indeed for your comments.\\
%	
%	
%	\review{ $\ldots$  It is important that you take into account their 
%	comments and 
%	evolve the paper accordingly. Please,  evolve the paper to make clear the 
%	defect model, hypothesis, limitations and readability}
%	
%	We offer clarifications to all the issues highlighted by the reviewers. In 
%	addition to these, we have made several key modifications to our paper. We 
%	have changed the title of our paper to reflect the changes we have made. In 
%	order to assist reviewers in tracking our changes, we have ensured all 
%	new additions are {\color{steel} highlighted in blue}. 
%	A brief summary of our changes are listed below:
%	\be
%	\item At the suggestion of Reviewers 1 and 2, we have included a section on 
%	the choice of datasets. Additionally, we have greatly expanded the section 
%	on defect prediction to highlight its importance and its relevance to our 
%	work.
%	\item To address comments by Reviewer~\#1 on how this work fits in with the 
%	body of knowledge, we have compiled a new section (see~\tion{prior}) on the 
%	previous attempts to address similar issues. 
%	\item Further, at the suggestion of Reviewer~\#1, we have included a 
%	section remarking on the key limitations of our work. It now appears as a 
%	new section (see \tion{future}).
%	\item Also, as a response to Reviewer~\#1's comments, we have modified the 
%	future work section to reflect the implications of our findings on 
%	\textit{technical debt}. 
%	\item We acknowledge Reviewer~\#2's comment that our initial submission 
%	lacks a formal introduction of software ``defects" and its relevance to 
%	code reorganization. In order to address this, we have attempted to 
%	clarify 
%	the interpretation of defects in our work. As for other issues related to 
%	defects, we have added a new section on the choice of datasets 
%	(see~\tion{dataset}).
%	\item Also, keeping in mind the suggestions of Reviewer~\#2, we have 
%	rewritten the research questions (especially, RQ1 and RQ5).
%	\item Additionally, at the suggestion of Reviewer~\#2, we clarify our 
%	descriptions of several figures included in this paper. Specifically, we 
%	expand on the importance of tuning which relates to \fig{j} (previously 
%	Figure 4). We also expand on the significance of \fig{multcomp} 
%	(previously 
%	Figure 8).
%	\item Finally, we have evolved our paper in the most appropriate areas in 
%	response to all the major and minor issues raised by both Reviewer~\#1 and 
%	Reviewer~\#2.
%	\ee
%	
%	\section*{Response to Reviewer~\#1}
%	
%	Thank you for your detailed comments. Our new draft contains many 
%	corrections, clarifications, and extensions as directed by your feedback.
%	All our changes are marked in the body and appears in {\color{steel} 
%	blue}.\\
%	
%	\review{I missed a section discussing possible implications for 
%	researchers 
%	and practitioners. How the results of this work contribute to future 
%	research activities in the area? How practitioners can benefit from the 
%	results achieved in the paper?}
%	
%	
%	You're quite correct, there was no future work section in the paper. The
%        following text
%	has been included in the revised submission and appears in~\tion{future} 
%	(see {\color{steel} Reviewer 1a}). 
%	
%	
%	\begin{quote}``Our research shows that it is potentially na\"{\i}ve to 
%explore 
%	thresholds in static code attributes in isolation to each other. 
%	This work clearly demonstrates how changing one necessitates changing 
%	other associated metrics. So, for future work, we recommend that 
%	researchers and practitioners look for tools that recommend changes to sets 
%	of code changes. When exploring candidate technologies, apart from XTREE, 
%	researchers may potentially use: (1) Association rule learning; (2) 
%	Thresholds generated across synthetic dimensions (eg. PCA); and (3) 
%	Techniques that cluster data and look for deltas between them. (Note: we 
%	offer XTREE as a possible example of this point).''
%	
%	``Additionally, we plan on extending our work by exploring scalable 
%solutions 
%	to achieve similar results in much larger datasets. After this, we shall 
%	look at applications beyond that of measuring static 
%	code attributes. For example, as an initial attempt, we have been looking 
%	at sentiment analysis in stack overflow exchanges to learn dialog pattern 
%	that most select for relevant entries.''
%        \end{quote}
%	
%	
%	\review{I also missed a section presenting the main limitations of 
%	the 
%	work. Although some words have been said about it, I believe it is 
%	important to have a more structured discussion on a specific section.}
%
%	You are quite correct that we have missed a section highlighting the key 
%	limitations of our work. In the revised paper, we have dedicated a section 
%	to discussing the 
%	limitations and future work (see {\color{steel} Reviewer1b} in 
%	~\tion{future}).\\
%	
%	\review{It would be interesting to have further discussion at the 
%	end 
%	indicating how this work complements the body of knowledge about code 
%	smells. Do 
%	reached results indicate a similar direction? contradictory? Does This work 
%	somehow confirms the results of other studies or points to new 
%	directions?}
%
%	Thank you for your comment, we admit the last version of the paper has 
%	an inadequate discussion on this matter. This revised version now includes 
%an 
%	expanded prior work section which places greater emphasis on these issues 
%	(see {\color{steel} Reviewer1c} in 
%	\tion{prior}). 
%	
%	As to your specific comment that this be included in the 
%	end, we feel our response to this recommendation is an important note on 
%	the state-of-the-art in this area. We have therefore added it towards the 
%	beginning of the paper instead, so it may premise the rest of our work.\\
%		
%	\review{$\ldots$ this work evaluated XTREE, a framework to 
%	evaluate whether a code reorganization is likely to have a perceivable 
%	benefit in terms of defect-proneness. It is fine to have this scope 
%	(defect-proneness) in terms of evaluation. However, it would be nice to 
%	have a discussion on why this characteristic (defect-proneness) is good to 
%	support the decision on code reorganization and/or how it could complement 
%	other characteristics.}
%	
%	You are quite right in pointing out that we need a better description of 
%	defect proneness. We have now added a section on defect-proneness and its 
%	relevance to our paper (please see content marked with {\color{steel} 
%	Reviewer1d} in~\tion{dataset}).\\
%
%	\review{$\ldots$ nowadays we are seeing a growing discussion on 
%	technical debt, 
%	that brings financial aspects (interest, principal, debt…) to the 
%	decision-making process on development activities. Could we use XTREE as a 
%	strategy to prioritize the payment of technical debt items?}
%	
%	Thank you for that suggestion. We do think XTREE can be used as a 
%	recommendation system to prioritize technical debt. In our revised paper, 
%	we expanded the introduction to highlight this possibility (see 
%	content prefixed with {\color{steel}Reviewer1e} in \tion{future}).\\
%	
%	\review{Finally, I have one last question: is there any reason for 
%	do not 
%	use the GQM template to state the goal of the study and also to define null 
%	and alternative hypotheses for the research questions?}
%
%        We can certainly do that if you wish. As to why we {\em didn't} do it,
%        this paper is clearly MSR-conference-style and not
%        ESEM-conference-style (GQM is less uses at MSR than ESEM).
%
%        To whether or not that is a ``good thing'' or not, we cannot say. What
%        we would say is that we think our use of stand-out boxes for research
%        findings makes our results easy to access within this paper.
%
%        That said, if the reviewer thinks this paper needs further structuring
%        to clarify our message then, of course, we would follow that direction.
%        
%%	\texttt{XXX}
%	
%	\section*{Response to Reviewer~\#2}
%	
%	Thank you for your detailed review. We have made several 
%	corrections, clarifications, and revisions as directed by your comments, 
%	this new draft is significantly improved thanks to your feedback. 
%	
%	\noindent All our 
%	changes are marked in the body and appears in 
%	{\color{steel} blue}.\\
%	
%	\review{The introduction talks about Fowler’s bad smells and 
%	refers to 
%	literature on the (often contradictory) effects of such smells. And Figure 
%	1 shows a list of bad smells. However, without making it clear, the paper 
%	continues to talk about smells but the real topic is not the smells but the 
%	metrics that are used to identify various smells. What’s the connection 
%	between whether a smell is bad or not and the threshold values of the 
%	various code metrics?}
%
%	Thank you for this comment. At your suggestion, we have significantly 
%	expanded \tion{dataset} in order to discuss the use of static code metrics 
%	with regards to code smells.\\
%	
%	\review{I also find it very difficult to understand the conceptual model of 
%	defects in this paper~\ldots}
%	
%	We do apologize for the inconvenience.
%Your remark clearly indicates that we need to further clarify our use
%        of the term.
%        So at your suggestion, we have 
%	dedicated a section to discussing the choice of dataset in \tion{dataset} 
%	(please see content marked with 
%	{\color{steel} Reviewer2a}).\\
%	
%	\review{\ldots~The concept of “number of defects (defect counts)” 
%	is fully mixed with the concept of “percent of classes with 
%	defects/defective modules/ presence or absence of defects”. What does it 
%	then mean to “reduce defects in our data sets”? Is it the total number of 
%	defects in the data set (system?) or the number of “infected modules” in 
%	the data set?}
%	
%	We have clarified this in \tion{dataset}. Briefly, with respect to the 
%	datasets used in this study, when we say, ``reduce defects in our data 
%	sets,'' we refer to 
%	reorganizing code such that our secondary oracle reports
%    that the number of infected modules (i.e., classes with 
%	$\texttt{nDefects}>0$) is reduced to having \textit{no defects}.
%    For notes on our {\em primary} and {\em secondary} oracle, see page2, 
%    column1, of this paper.
%	
%	In response to your  comment, we have expanded \tion{dataset}, to 
%	better explain this in much greater detail (please see content marked with 
%	{\color{steel}Reviewer2b} in \tion{dataset}). \\
%
%   \review{ Section 2 discusses the idea of why not just ask developers
%     about the effect of code smells when the research literature is
%     contradictory. The authors argue that practitioners
%     should not be expected resolve contradictions. My point is that it is
%     so obvious that most of Section 2 should be deleted. Figure 1 as part
%     of a related work section may remain.}
%
%       This is an interesting comment since it is the {\em opposite} of the 
%feedback we got on a earlier draft of this paper. In fact, we had
%       a certain senior SE person (who the reviewer might actually know....) 
%demanding ``why not just use best practices from the literature?''.
%       That comment lead to the Fig1 survey.
%
%
%       That said, we quite take your point that our current 
%       section~\tion{prelim} is far 
%       too long. For this draft, prompted by
%       your comment, we have cut its length in half.\\
%	
%	\review{\ldots~How does a log of defects look 
%	like? What kind of information is recorded? ...  In case 
%	four new modules are developed, is there then also a log 
%	history that shows how the total number of modules in the system correlates 
%	with the total number of defects? Are we talking about total number of 
%	defects or only the number of “infected modules”?}
%
%	
%	To answer these issues, we have provided a sample defect data set in 
%	\fig{example}. The example shows a few rows of data from Ant 1.3 
%	containing: (1) Module 
%	name; (2) 20 CK-Metrics; and (3) Defects (as a count of raw defects and a 
%	boolean variable). Note that \fig{j} lists all the remaining datasets and 
%	they all have been formated in the same way. \\
%	
%	\review{From RQ1: ``This code reorganization will start with some initial 
%	code base that is changed to a new code base. For example, if the bad smell 
%	is loc $>$ 100 and a code module has 500 lines of code, we reason 
%	optimistically that we can change that code metric to 100. Using the 
%	secondary verification oracle, we then predict the number of defects in 
%	new.'' What is the idea here?}
%	
%	Thank you for the question. Your observation regarding this --- \emph{Is 
%	the point that a log 
%	history of defects has shown that modules 
%	with more than 100 loc have more defects (per lines of code?) than smaller 
%	modules, and then the action is to reduce the size of that module?} --- is 
%	accurate.  We have now modified the content in corresponding section to 
%	further explain this in \textbf{RQ1} (please see content marked with 
%	{\color{steel} Reviewer2c} in \tion{setup}).\\	
%	
%	
%	\review{RQ1 is  ``which of the methods is most accurate?'' without 
%	presenting 
%	the methods. They are just referred to in three other papers that probably 
%	describe them. What are your selection criteria for comparing the tool (or 
%	framework or system as you also call it) XTREE with exactly these methods?}
%	
%	Thank you for your comment. We have fixed the description of \textbf{RQ1} 
%	to be more specific (please see content marked with 
%	{\color{steel} Reviewer2d} in \tion{rqs}). As to selecting primary change 
%	oracles, we undertook a survey of literature to identify commonly used 
%	methods to do this. We found three other techniques: CD from a previous 
%	work, VARL based thresholds~\cite{Shatnawi10}, and Statistical 
%	thresholding~\cite{Alves2010}.
%	\\
%
%        \review{It is stated that this paper reports a case study. I know that 
%within the SW community is its common to use the term case study to denote 
%just 
%a demonstration of an example performed by the researchers. But in more mature 
%disciplines, which we should aim to become a member of, “case study” has a 
%certain meaning (e.g. Yin 2003). It would mean an evaluation in a real 
%software 
%development context. This is note the case here. See also the work by Runeson 
%and Host 2009 on case studies in software engineering.}
%
%        Thank you for that comment. We can show that our definition of
%        ``case study'' is aligned with how Per Runeson uses the term.
%        In 2013, we were  working on revising a data mining paper for TSE paper
%        where Runeson was the associate editor. He pushed us hard for better 
%terminilogy and definitions, including our term ``case study''. To address his 
%concerns, we wrote the following
%        notes about ``case studies'' and data mining papers. Note that
%        he accepted the point offered below and accepted the paper.
%
%
%        \begin{quote}
%
%As we read standard texts on empirical software engineering
%(e.g. Runeson \& Host\footnote{P. Runeson and M. Host, ``Guidelines for 
%conducting and reporting
%case study research in software engineering,'' Empirical Software
%Engineering, vol. 14, pp. 131–164, 2009} ) the term ``case study'' often 
%refers to some act which includes observing or changing
%the conditions under which humans perform some software
%engineering action.
%
%In the age of data mining and modelbased
%optimization this definition should be further extended
%to include case studies exploring how data collected from
%different projects can be generalized across multiple projects.
%As Cruzes et al. comment:
%\begin{quote}
%``Choosing a suitable method for synthesizing evidence
%across a set of case studies is not straightforward...
%limited access to raw data may limit the ability
%to fully understand and synthesize studies.\footnote{P. R. M. H. Daniela 
%Cruzes, Tore Dyba, ``Case studies synthesis:
%Brief experience and challenges for the future,'' in ESEM’11: the
%International Symposium on Empirical Software Engineering and Measurement,
%2011.}''
%\end{quote}
%        \end{quote}
%        Note that the above quote from Cruzes et al. is almost a summary of the
%specific goals of this paper: given limited amounts of software
%project data, how can we rank bad smells such as to avoid making unecessary, 
%or bad, changes.
%\\
%%\clearpage
%
%\review{Regarding case study, what kind of work remains before the proposed 
%tool could be used by practitioners?}
%
%We need to address a scale-up problem (which is the current focus of Mr. 
%Krishna's Ph.D. work) and once that is done,
%we will make this a Python package freely available to the world on Windows,
%Linux, and Mac machines via the simple command `\texttt{pip install xtree}'.
%After that is installed, the code would search a directory of project data to 
%automatically generate the figures of this paper.\\
%        
%	\review{What’s the difference between tool, framework, and method in this 
%	paper?}
%		
%	Thank you for pointing that out. We offer the following definitions: (1) 
%	Framework: A basic structure underlying recommending reorganization. It 
%	comprises of a primary change oracle and a secondary verification oracle; 
%	(2) Method: Refers to how the primary change oracle offers these 
%	recommendation. 
%	In this work it may be based on Cluster Deltas (XTREE) or threshold based 
%	(Shatnawi and Alves); and (3) Tool: Comprises of any one primary change 
%	oracle (XTREE) and a secondary verification oracle (Tuned Random Forest). 
%	
%	We may have used these interchangeably in the first draft of our paper. 
%	This has been fixed in this revision.\\
%	
%	\review{How does this work related to the work by Arcelli Fontana, in 
%	particular: Arcelli Fontana, F., Mantyla, M.V., Zanoni, M. et al. Comparing 
%	and experimenting machine learning techniques for code smell detection, 
%	Empir Software Eng (2016) 21: 1143. doi:10.1007/s10664-015-9378-4?}	
%	
%	Thank you for the reference. Our work differs from this specific paper in 
%	one 
%	key aspect --- we attempt to assist reorganization of code and prevent 
%	needless reorganization while they focus on 
%	detecting code smells using machine learning techniques. Our work is much 
%	closer to other work by Arcelli Fontana~\cite{font1}. We discuss this 
%	in~\tion{prior}. \\
%	
%	
%	\review{Improving on one metric may cause degradation 
%	on another one. This issue could have been much more spelt out with good 
%	examples in the paper. It's stated that XTREE “recommends” 
%	(or “suggests”) increasing coupling while reducing LOC of a module. Sure, 
%	if you split a module into several smaller modules, or move code from one 
%	large module to other, smaller modules, usually the overall coupling will 
%	increase.  But isn't that an avoidable consequence that will occur 
%	implicitly in the process of module splitting or moving code between 
%	modules? The way it’s formulated now gives the impression that the 
%	programmers should follow the recommendation of increasing the coupling, 
%	that is, as if it’s a conscious action. Or am I missing the point?}
%	
%	You are quite right, we have now rewritten associated text with 
%	\textbf{RQ5} in \tion{conjunct} to better explain 
%	the underlying connectedness of the metrics ({\color{steel} Reviewer2e} in 
%	\tion{conjunct}). 
%	
%	To summarize, we were trying to convey the following information with this 
%	specific example:
%	
%	\be
%	
%	\item
%	Attempting to reduce certain code metrics (like LOC) necessitates 
%	increasing other metrics. Any recommendation that fails to respect these 
%	``co-changes'' may not the practical to follow.
%	\item  XTREE is aware of 
%	the relationship between metrics and always recommends changes to 
%	conjunctions of metrics. These changes are pragmatic in that XTREE 
%	sometimes suggests the same metric be either increased or decreased based 
%	on the dataset. As an example, consider \fig{changes} in Ant coupling 
%	between objects (CBO) has to be reduced while in Lucene CBO has to be 
%	increased.
%	\ee
%	
%	Developers are now aware of these interconnected changes. They can proceed 
%	to make these changes because of the historical evidence of its 
%	effectiveness.\\
%	
%	
%	\review{In Section 4: ``It can be difficult to judge the effects of 
%	removing 
%	bad smells. Code that is reorganized cannot be assessed just by a rerun of 
%	the test suite since such reorganizations may not change the system 
%	behavior (e.g., refactorings).'' Isn't the point about removing bad smells 
%	to improve the code without changing the behavior (refactorings)? Why 
%	cannot a test suite be run before and after if the behavior is not changed?}
%	
%	It is true that refactoring improves the code by performing behavior 
%	preserving modifications. Evaluating this code with test suites that are 
%	designed to 
%	identify faults would not work for three reasons: (1) Test suites may not 
%	be 
%	designed to identify code smells, they only report pass/fail based on 
%	whether or not a specific module runs. It is entirely possible that a test 
%	case may pass for code that contains one or more code smells; (2) While 
%	smells are certainly symptomatic of design flaws, not all smells cause the 
%	system to fail in manner suitable for identification by test cases; and (3) 
%	It make take a significant amount of effort to write new test cases that 
%	identify bad smells, especially for stable software.
%	
%	Finally, in our work we tackle reorganization which subsumes refactoring. 
%	Since not all reorganization efforts comprise of refactoring, that makes it 
%	difficult to assert when test case will pass or fail. Thus, using test 
%	suites is not a reliable option. 
%	

>>>>

\definecolor{steel}{rgb}{0,0,0}
\definecolor{steel2}{rgb}{.11, .11, .7}
\definecolor{Gray}{rgb}{0.88,1,1}
\definecolor{Gray}{gray}{0.85}
% \usepackage[svgnames]{xcolor}
\usepackage[framed]{ntheorem}
\usepackage{framed}
\usepackage{tikz}
\usetikzlibrary{shadows}
%\newtheorem{Lesson}{Lesson}
\theoremclass{Lesson}
\theoremstyle{break}

@@

			\noindent
			{\bf Results: }Code modules that are changed in response to XTREE's 
			recommendations contain significantly fewer defects than 
			recommendations from previous studies. Further, XTREE endorses 
			changes to very few code metrics, so XTREE requires programmers to 
			do less work. Further, XTREE's recommendations are more 
            responsive to the particulars of different data sets. Finally 
            XTREE's recommendations may be generalized to identify the most 
            crucial factors affecting multiple datasets (see the last figure in 
            paper).

			\noindent
			{\bf Conclusion: }
			Before undertaking a code reorganization based on a bad smell 
			report, use a framework like XTREE to check and ignore any such 
			operations that  are useless; i.e. ones which lack evidence in the 
			historical record  that it is useful to make that change. Note 
			that this use case applies to both manual code reorganizations 
			proposed by developers as well as those conducted by automatic 
			methods.

@@

	In terms of concrete recommendations for
		practitioners, we say {\em look before you leap}:
		\bi
		\item Before doing  code reorganization based on a bad smell 
		report$\ldots$ 
		\item $\ldots$ check and discourage any code reorganization   for which 
		there 
		is no proof
		in the historical record that the change improves the code.
		\ei
		Aside: this recommendation   applies to both manual code 
		reorganizations proposed by developers
		as well as the code reorganizations conducted by automatic 
		methods~\cite{mkaouer2015many}. That is, XTREE could optimize automatic
		code reorganization by discouraging reorganizations for useless goals.

	{\color{steel2} (Reviewer1a)
	Beside this introduction, the rest of this paper is formatted as follows. 
	\tion{prior0} relates the current work to the prior literature on bad 
	smells and code reorganization efforts. In \tion{dataset}, we 
	discuss the choice 
	of our datasets and briefly describe it's structure. \tion{bst} details the 
	frequently used techniques on leaning bad smell thresholds to assist 
	reorganization. Specifically, 
	\tion{xtreextree} and \tion{xtreextree2} describe our preferred method for 
	performing code reorganizations. Our experimental setup and evaluation 
	strategies are presented in \tion{setup}. The results and corresponding 
	descriptions are available in \tion{results}. The future work and the 
	reliability of our finding are available in \tion{future} and \tion{valid} 
	respectively. Finally, the conclusions are presented in \tion{conclusions}. 
}

	\section{Relationship to Prior Work }
	\label{sect:prior0}
	{\color{steel}	
	\subsection{Prioritizing Reorganization Efforts}
	\label{sect:prior}

@@

	\subsubsection{XTREE: Recommending Code Reorganizations}
		\label{sect:xtreextree2}
	Using the training data construct a decision tree as suggested above.

@@

	The effect of tuning and using SMOTE were remarkable.The rows 
	\colorbox{celadon}{marked with a $\star$} in \fig{j} show data 
	sets whose performance was improved by these techniques. For 
	example, in {\em poi}, the recall increased by 4\% while the false alarm 
	rate dropped by 21\%. In \textit{Ivy, Jedit, Lucene,} and \textit{Xalan} 
	there was a 
	significant improvement in one measure (recall or false alarm) with no 
	deterioration in the other measure. Finally, in \textit{Poi} and 
	\textit{Ant} there was a significantly large improvement in one metric with 
	a very small deterioration in the other. }

	{\color{steel2} (Reviewer2a) However, as expected, we found that some 
	datasets (xerces, 
	xalan, log4j, 
	...) were not responsive to our tuning efforts. Since, we could not salvage 
	all the data 
	sets, we eliminated these data sets for which we could not build 
	an adequately performing Random Forest classifier with $\mathit{pd}\ge 60 
	\wedge \mathit{pf} \le 30$\%. Thus, our analysis uses the {\em jedit, ivy, 
	ant, lucene} and {\em poi} data sets for evaluating recommended changes.}

@@

	\input{rq2.tex}
	\section{Results}
	\label{sect:results}

@@

	{\color{steel2} (Reviewer2b) This is quite significant for practitioners 
	attempting to perform code reorganization to similar projects without a 
	historical log. They can use these findings as guide to: (1) deprecate 
	changes the show no demonstrable benefits; and (2) not limit themselves to 
	reducing values all the metrics because an increase can sometimes be more 
	beneficial.}

@@

        In this work, both the primary change oracle and the secondary 
        verification oracle 
        used OO metrics in conjunction with the number of associated defects to 
        operationalize code smells. We note this goal can very easily be 
        replaced by other quantifiable objectives. For example, there is much 
        research on \textit{technical debts} in recent years.
        The notion of technical debt reflects the extra work arising
        from developers making pragmatic short-term decisions
        that make it harder, in the long-term, to maintain the software.
        A study by 
        Ernst et al.~\cite{ernst15} showed that practitioners agree on the 
        importance of the issue but existing tools are not currently helpful in 
        managing the debts. A systematic literature survey conducted by Li et 
        al.~\cite{li15td} report that dedicated technical debt management (TDM) 
        tools are needed for managing various types of technical debts. 
        {\color{steel2} (Reviewer1b) Recently Alves et al.~\cite{alves2016} 
        conducted an 
        extensive mapping study on the identification and management of 
        technical debt. They identified several types of debts over the past 
        decade and found that bad smells of the sort discussed in this paper 
        are very well known indicators of design debt. In fact, they happen to 
        be few of most 
        frequently referenced kinds of debts. 
        XTREE 
        could be adapted for this purpose by supporting decisions if and when a 
        technical debt item should be paid off -- providing that there existed
        a working ``secondary oracle'' (of the kind we define in our introduction)
        that can recognize quick-and-dirty sections of code.}

@@

	\section{Conclusions}
	\label{sect:conclusions}
	How to discourage useless code reorganizations?
	We say:
        \begin{quote}{\em Ignore those changes
            not supported by the historical log of data from
	the current project.}\end{quote}
	When that data is not available (e.g. early
	in the project) then developers could use the general list of
	bad smells shown in \fig{smells}. However,
	our results
	show that  bad smell detectors are most
	effective when they are based
	on a small handful of code metrics (as done by XTREE).
	Hence, using all the bad smells of \fig{smells} may not be optimal.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%%% RESPONSE TO REVIEWERS

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\pagebreak
	\newpage
	\appendix
	\renewcommand*{\thesection}{\Alph{section}}
	\nobalance
	\section*{RESPONSE TO REVIEWERS}
	\section*{Comments from the editor}
	\review{The reviewers recognized the improvements at the same time they 
	raised some minor concerns regarding the content of the paper. Please, 
	prepare an evolved version for a next verification. Use the reviewers' 
	suggestions to make all changes needed.$\ldots$}

	Thanks again for your comments. We have addressed all the concerns raised 
	by the reviewers.

	\review{Reviewer 1 suggested an additional reference that you have the 
	freedom to 
	consider it or not, depending on your interest on it. All other suggestions 
	deserve your attention. }

	We have taken into account the paper suggested by the reviewer. We found it 
	very relevant to our work and have added it to our review in \S7.

	\section*{Response to Reviewer \#1}

	\review{Initially, I´d like to thank the authors for having appropriately 
	addressed the comments from the first review. Now I have just minor 
	comments on the paper:}

	Thank you for your comments. We have taken your remarks into account and 
	have made appropriate changes to the paper.\\

	\review{I missed a last paragraph on the introduction presenting the 
	structure of the paper (for example, ``Besides this introduction, Section 2 
	presents\ldots. Next, Section 3 discusses…'').}

	Thank you highlighting that. We have now added a paragraph toward the end 
	of \S1
	presenting the structure of the paper. Kindly see content marked 
	{\color{steel2} Reviewer1a}.\\

	\review{On Section 7, when you relate your approach with technical debt, 
	I´d like to suggest you to also consider the mapping study cited below 
	\ldots}

	Thank you for recommending this paper. We have used this citation to expand 
	our \S7 accordingly. Please see content marked 
	{\color{steel2} Reviewer1b} in \S7.
	\newpage
	\section*{Response to Reviewer \#2}

	\review{I’m happy with the great job the authors have done with the 
	responses.}

	Thank you very much for your comments. We have now addressed the comments 
	in this 
	revised version.\\

	\review{I believe you missed my point, ``Your example is the most favorable 
	example from your point of view. It is one of only two of the eight data 
	sets that improved on both pd and pf.'' }

	Thank you for that clarification. We see the issue. We have now added text 
	to section \S5.2.1 providing example of failed cases in addition to 
	positive sample. Kindly see content marked {\color{steel2}Reviewer 2a} in 
	\S5.2.1.\\

	\review{I still find the last two sentences in the abstract odd: ``This 
	recommendation assumes that there is a historical record. If none exists, 
	then the results of this paper could be used as a guide.''}

	Thank you pointing that out. \textit{We have now removed these lines from 
	the abstract} 
	and have added it to relevant section in the body of paper. Briefly, we 
	intended to 
	convey the following with figure 9:
	\bi
	\item Some metrics (like loc) are best minimized as much as practically 
	possible;
	\item Developer need not hesitate leaving some metrics (like certain types 
	of coupling) 
	untouched or even maximize them when that's an option.
	\ei

	Please see content marked {\color{steel2} Reviewer2b} in \S6.5.
\end{document}
